\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{Final Report Manual Gap Review}
\author{Review Bot}
\date{\today}

\begin{document}
\maketitle

\section{Executive Summary}
The final report has a strong modular skeleton, but misses deep "why research-grade" logic, relies too heavily on generic TPS statements without gas/workload nuance, and asserts empirical findings where completed logs are currently absent. This review compares the report against the provided source documents.

\section{Current Report Strengths}
- Modular directory structure.
- Covers basic background (Trilemma, ZK Proofs).
- Implements core chapters (Methodology, Results, Discussion).

\section{Missing Content Compared with Source Documents}
\begin{itemize}
    \item \textbf{Building a Research ZK-Rollup.docx}: Missing the explicit four computational complexity/hardware wall pain points. Missing the core transfer-centric STF checks (signature, balance, nonce, Merkle).
    \item \textbf{deep-research-report (3).md}: Missing the framing of Ethereum as the first broadly adopted general-purpose programmable blockchain. Missing the difference between observed ~24 TPS and gas-based ~238 TPS upper bound.
\end{itemize}

\section{Short / Weak Sections}
\begin{itemize}
    \item 1.1 Motivation: Too brief on Ethereum choice vs fast L1s.
    \item 2.1.7 Ethereum Scalability Limitations: Too brief on gas limit vs real workload complexity.
    \item 7.4 Prover: Missing explanation of hardware wall and mock delay isolation.
    \item 9 Results: Claims findings despite missing output logs.
\end{itemize}

\section{Risky or Contradictory Claims}
- Abstract implies completed rigorous benchmarking despite missing results files.
- Avoid "secure vs insecure" simplistic claims when comparing L1s.

\section{Citation and Bibliography Issues}
- Resolved in patch, but originally had unresolved [?] tags in intro.

\section{Required Tables to Add}
- Ethereum vs High-Throughput L1s
- ZK-Rollup Cost Model
- Why Research-Grade Instead of Production-Grade
- Prior Work Summary
- Results Availability Summary

\end{document}
