\chapter{Individual Contributions}
\label{ch:individual_contributions}

This research project was designed, implemented, and evaluated as a collaborative team effort. The following table outlines the primary areas of responsibility. 

\textit{Note: As this is a highly integrated system, many tasks overlapped, and this matrix serves as a broad overview of primary ownership based on the repository history.}

\begin{table}[H]
\centering
\caption{Team Contribution Matrix}
\label{tab:contributions}
\small
\begin{tabularx}{\textwidth}{l X}
\toprule
\textbf{Team Member} & \textbf{Primary Focus Areas (To be verified by the team)} \\
\midrule
Fernando T.H.L. & Sequencer architecture, Domain-Driven Design integration, JSON-RPC API, and batching logic implementation. \\
Gamage M.S. & Submitter architecture, Layer-1 integration, Data Availability formatting (Calldata/Blob), and Saga workflow implementation. \\
Lishan S.D. & Executor adaptation, gRPC communication layer, state transition engine configuration, and Prover backend integration. \\
Perera M.V.D.P.D.S. & Benchmarking suite, Workload Generator (Python), Data Tools analytics pipeline, Smart Contract testing, and orchestration scripts. \\
\bottomrule
\end{tabularx}
\end{table}

\chapter{Conclusion and Future Work}
\label{ch:conclusion}

\section{Conclusion}
This report demonstrated the design, implementation, and evaluation of a modular ZK-Rollup benchmarking prototype. By cleanly isolating the sequencing, execution, proving, and submission stages, the framework allowed for a systematic analysis of the fundamental throughput--latency--cost trade-offs inherent in Layer-2 scaling solutions. The empirical observations highlight the severe impact of batch sizes, data availability modes (specifically the efficiency gains of EIP-4844 blobs over calldata), and parameterized proof generation delays on overall system performance.

\section{Future Work}
Future research directions include:
\begin{itemize}
    \item Replacing the parameterized mock prover with a fully integrated, real cryptographic prover cluster under heavy, parallelized load.
    \item Transitioning from synthetic Poisson-based load generators to trace-driven workloads based on historical mainnet dataset replays, which would provide greater external validity.
    \item Implementing dynamic, adaptive batching policies that automatically adjust based on real-time Layer-1 fee conditions and mempool depth.
\end{itemize}
