\section{Motivation}
\label{sec:motivation}

Blockchain adoption has grown exponentially across various sectors, including finance, supply chain management, and decentralized applications (dApps). However, as the user base and transaction volumes expand, the underlying networks face significant scalability challenges. Ethereum Layer-1, a broadly adopted programmable settlement layer, provides strong security and decentralization but remains constrained by limited throughput, network congestion, and severe fee volatility \cite{buterin2014ethereum}. Its sequential execution model and consensus mechanism traditionally limit the network to approximately 15 transactions per second (TPS).

This fundamental limitation reflects the widely recognized blockchain trilemma—or in some contexts, quadrilemma—which posits that decentralized systems must balance scalability, security, and decentralization (and often privacy/trust), and cannot maximize all simultaneously \cite{fu2024trilemma}. Consequently, a robust scaling strategy is required to achieve high transaction throughput and low latency without compromising the security guarantees of the base layer.

Ethereum's current scaling direction relies heavily on Layer-2 (L2) rollups. Rollups move transaction execution off-chain, grouping many off-chain transactions into large batches, while continuing to use Layer-1 (L1) for settlement, verification, and data availability. This approach amortizes the fixed L1 submission costs across multiple transactions, effectively increasing throughput while retaining Ethereum as the ultimate security layer.

Within this rollup-centric design space, Zero-Knowledge (ZK) Rollups are particularly attractive. They bundle hundreds or thousands of off-chain transfers into a single transaction and submit cryptographic validity proofs (such as zk-SNARKs or zk-STARKs) that allow Layer-1 smart contracts to mathematically verify off-chain state transitions. This avoids the need for L1 to re-execute every transaction, preserving the base layer's security model while significantly reducing the computational burden on L1.
Ethereum is a general-purpose programmable blockchain with a built-in Turing-complete programming language for smart contracts \cite{buterin2014ethereum, ethdocs_contracts}. While Ethereum provides strong security and decentralization \cite{ethdocs_pos}, its observed transactions per second (TPS) is around 20-24 TPS \cite{etherscan_tps}, compared to high-throughput chains like Solana which can reach over 1,000 TPS \cite{chainspect_tps}. However, Ethereum's value lies in its secure settlement layer, making L2 rollups the primary scaling direction \cite{ethdocs_scaling}.
