\section{Introduction}

\subsection{Motivation}

Ethereum Layer-1 provides strong security and decentralization but remains constrained by limited throughput, congestion, and fee volatility~\cite{buterin2014ethereum,wood2014ethereum}. This limitation reflects the blockchain trilemma, where decentralized blockchain systems must balance scalability, security, and decentralization rather than maximizing all three simultaneously~\cite{fu2024trilemma}. Ethereum's current scaling direction therefore relies heavily on Layer-2 rollups, which move transaction execution off-chain while using Layer-1 for settlement, verification, and data availability~\cite{ethereum_scaling_docs,ethereum_data_availability_docs}.

Within this rollup-centric design space, ZK-Rollups are particularly attractive because they submit cryptographic validity proofs that allow Layer-1 contracts to verify off-chain state transitions without re-executing every transaction. This preserves the base layer's security model while reducing the amount of computation performed directly on Layer-1.

\subsection{Problem Statement}

Practical ZK-Rollup performance is shaped by several interacting factors, including batch formation, sequencer scheduling, data availability footprint, Layer-1 submission cost, and proof-generation overhead~\cite{habib2025bottlenecks,chaliasos2024benchmarking}. These factors do not affect performance independently: increasing batch size may reduce amortized submission cost while increasing queueing delay, changing the data availability path may reduce posting cost while changing finalization behavior, and proof-generation overhead may dominate end-to-end latency under larger or more complex batches.

The research problem addressed in this paper is the lack of a compact and reproducible experimental framework for isolating how batching, sequencing, proof-delay, and data availability choices affect ZK-Rollup throughput, latency, finalization time, and cost behavior under comparable workloads.

\subsection{Research Gap}

Existing studies provide valuable insights into deployed rollups, public datasets, data availability costs, sequencing behavior, and proof-generation bottlenecks. However, most prior work either analyzes production systems after deployment or studies specific rollup components in isolation. Production ZK-Rollups are optimized for reliability, compatibility, and user-facing deployment, but their internal batching, sequencing, proving, and data availability policies are difficult to modify under a fixed benchmark harness.

As a result, there remains a gap for a modular research prototype that can vary batching, sequencing, data availability, and proof-delay parameters independently while replaying comparable workloads. Addressing this gap is important for understanding how configuration choices shift ZK-Rollup throughput, latency, finalization time, and cost behavior before such choices are applied in production systems.

\subsection{Research Questions, Objectives, and Outcomes}

This work is guided by the following research questions:
\begin{enumerate}
    \item How can a modular ZK-Rollup prototype be designed to support controlled benchmarking of batching, sequencing, state execution, proof handling, and data availability choices?
    \item How do variations in batching strategy, sequencing policy, and data availability mode shift end-to-end performance across throughput, latency, data footprint, and cost dimensions?
    \item How can parameterized proof-delay measurements help isolate proving-stage effects from sequencing, execution, and Layer-1 submission overhead?
\end{enumerate}

The primary objective is to design, implement, and systematically benchmark a modular ZK-Rollup research prototype under controlled synthetic workloads. The expected outcomes include a reproducible experimental framework, preliminary insights into throughput--latency--cost trade-offs, and an open-source benchmarking harness to support future Layer-2 scalability research.

\subsection{Contributions}

The main contributions of this work are:
\begin{itemize}
    \item We design and implement a modular ZK-Rollup research prototype with separated sequencer, simplified state-transition executor, prover interface, submitter, smart contract, and data availability components.
    \item We expose configurable batching, sequencing, and data availability policies to support controlled benchmarking under comparable workload conditions.
    \item We define a reproducible methodology using controlled synthetic workloads and parameterized proof-delay measurements to compare relative behavior across configurations.
    \item We formulate a cost-equivalent dynamic batching model as an analytical extension for studying adaptive batch-size selection under changing workload and fee conditions.
    \item We analyze preliminary throughput--latency--cost trade-offs and study bottleneck trends under mock/parameterized proving delay to guide future ZK-Rollup optimization.
\end{itemize}