\section{Background}

\subsection{Ethereum Scalability and Rollups}

Ethereum's rollup-centric scaling roadmap relies on Layer-2 systems that move execution off-chain while using Layer-1 for settlement, verification, and data availability~\cite{ethereum_scaling_docs,ethereum_data_availability_docs}. By grouping many off-chain transactions into batches, rollups amortize Layer-1 submission and verification costs across multiple transactions while retaining Ethereum as the security and settlement layer.

ZK-Rollups extend this model by using validity proofs to attest to the correctness of off-chain state transitions. Depending on the system design, these proofs may be based on SNARK- or STARK-style constructions, including pairing-based arguments such as Groth16 and transparent proof systems such as STARKs~\cite{groth2016snark,ben2018stark}. In production systems, such proof systems allow Layer-1 contracts to verify compact proof artifacts rather than re-executing every transaction.

\subsection{ZK-Rollup Performance Factors}

ZK-Rollup performance is shaped by both cryptographic and systems-level factors. Proof generation can become a computational bottleneck, while batching affects queueing delay, finalization time, and cost amortization~\cite{habib2025bottlenecks,chaliasos2024benchmarking}. Sequencer ordering also affects latency and fairness because the sequencer determines transaction inclusion order and batch construction~\cite{motepalli2023sequencers}.

Data availability is another major performance and cost factor. Posting rollup data through calldata provides strong availability through Ethereum, but it can be expensive. EIP-4844 introduces blob-carrying transactions where large rollup data are made available through blob space rather than permanent calldata. The EVM cannot directly access blob contents, but commitments to blob data are accessible, making blobs suitable for rollup data availability rather than general contract execution data~\cite{eip4844,ethereum_data_availability_docs}. This changes the cost structure of rollup submission and motivates separate evaluation of calldata and blob-based DA paths~\cite{saif2024dataavailability,lavaur2023modular}.

\section{Related Work}

\subsection{Rollup Benchmarking and Public Datasets}

Existing studies analyze production rollup traces, public datasets, deployed systems, cost behavior, and rollup bottlenecks~\cite{silva2025zksyncdataset,chaliasos2024benchmarking,habib2025bottlenecks}. These studies provide valuable insight into real-world rollup behavior, but they primarily observe existing deployments. As a result, they are less suited for isolating the causal impact of individual configuration choices, because batching rules, sequencing policies, proof-delay behavior, and DA modes cannot always be independently modified under identical workloads.

\subsection{Positioning of This Work}

Prior work provides valuable insight into deployed rollups and production traces, while the proposed prototype focuses on controlled configuration-level experimentation under comparable synthetic workloads.

\begin{table}[t]
\centering
\caption{Positioning of the proposed prototype against production rollups}
\label{tab:positioning}
\scriptsize
\begin{tabular}{p{1.8cm}p{1.3cm}p{1.5cm}p{1.6cm}}
\toprule
System & Main Goal & Exposed Internals & Benchmark Focus \\
\midrule
zkSync Era & Production L2 & Limited externally & Public deployment metrics \\
Polygon zkEVM & EVM compatibility & Limited externally & zkEVM execution and proving \\
Starknet & Production validity rollup & Limited externally & Cairo-based execution \\
Proposed prototype & Research benchmarking & Configurable & Batching, sequencing, DA, proof delay \\
\bottomrule
\end{tabular}
\end{table}

As summarized in Table~\ref{tab:positioning}, the proposed prototype is complementary to production rollups rather than a replacement for them. Production systems prioritize reliability, compatibility, and user-facing deployment, whereas the proposed prototype prioritizes controlled experimentation and observability. By exposing batching, sequencing, DA, and proof-delay controls, the prototype enables repeatable studies of how individual design choices shift throughput, latency, and cost behavior.