\section{Conclusion and Future Work}

This paper presented a modular ZK-Rollup research prototype for controlled benchmarking of Layer-2 scalability bottlenecks. By separating sequencing, execution, proof handling, submission, and data availability concerns, the framework enables configuration-level experiments over batching, ordering, DA mode, and parameterized proof-delay settings. The preliminary synthetic evaluation demonstrates how these choices shift throughput, latency, data footprint, and cost behavior, while avoiding claims of production mainnet performance.

\subsection{Limitations}
The dynamic batching model currently depends on estimated or parameterized values for proof delay, blob fee, and user latency preference. Therefore, its selected batch size should be interpreted as a heuristic operating point rather than a globally optimal policy. More accurate calibration requires real prover benchmarks, serialized DA payload measurements, and sensitivity analysis over different \(\gamma\) values.


The proposed prototype is a research tool, not a production-ready rollup or a full zkEVM. The current executor supports simplified transfer-style state transitions rather than general smart contract execution. The evaluation relies on synthetic workloads in a local or controlled test environment, and therefore may not capture complex DeFi interactions, adversarial transaction patterns, or mainnet network conditions. In addition, the mock-prover mode simulates computational delay and does not capture the full cryptographic complexity, memory usage, or hardware sensitivity of real proof generation.

\subsection{Future Work}
Future work will integrate the dynamic batch-size controller directly into the sequencer policy layer and evaluate it against fixed-size, fixed-interval, and soft-cap batching. The evaluation will include sensitivity analysis over the impatience factor \(\gamma\), empirical calibration of \(P(N)\) using real prover measurements, and DA payload measurements for calldata and EIP-4844 blob submission.


Future work will focus on integrating and benchmarking full cryptographic prover execution to measure actual proving latency and hardware overhead. The framework will also be extended with trace-driven workloads, a complete trustless deposit and withdrawal path, decentralized sequencing experiments, and real off-chain DA backends such as Celestia or Avail. Finally, releasing the benchmark harness, configurations, and datasets as a public reproducibility package would support broader comparison of ZK-Rollup design choices.