\section{Executor}
\label{sec:executor}
The Executor serves as the host-side state transition and proving coordinator.

\begin{itemize}
    \item \textbf{Language:} Rust (requires \texttt{nightly-2024-08-01} toolchain).
    \item \textbf{Execution Role:} Adapted from open-source zkSync components, it processes a \texttt{publish\_batch} request via gRPC. It parses and normalizes transactions, and executes the state transition function (STF) using a \texttt{SimpleTransactionEngine} backed by a \texttt{RocksDbStateManager}.
    \item \textbf{Prover Integration:} After execution, it builds an \texttt{ExecutionTraceV1} and invokes the prover backend to generate proof artifacts. 
    \item \textbf{Output:} It emits an enriched batch payload (containing the DA commitment and proof) back to the Submitter and logs execution metrics.
    \item \textbf{Limitations:} The executor is a simplified state-transition engine tailored for transfer-style workloads and Merkle state updates. It is not a full EVM or zkEVM. Furthermore, there is a known upstream issue where \texttt{risc0\_prover} throws an `Elf parse error` during guest execution in certain configurations, requiring specific test bypasses during CI.
\end{itemize}
\begin{table}[ht]
\centering
\caption{Core Transfer-Centric STF Checks}
\begin{tabular}{|p{3cm}|p{4cm}|l|p{4cm}|}
\hline
\textbf{Check} & \textbf{Purpose} & \textbf{Data Type} & \textbf{Prototype Interpretation} \\ \hline
Signature Validity & Prevent spoofing & Public & Mocked in benchmark runs \\ \hline
Balance Sufficiency & Prevent double spend & Private (State) & Merkle tree verified \\ \hline
Nonce Correctness & Prevent replay attacks & Private (State) & Strict increment \\ \hline
Merkle Transition & Ensure state integrity & Public (Roots) & Forms validity proof core \\ \hline
\end{tabular}
\end{table}

The transfer-centric research logic simplifies execution, making full EVM equivalence out of scope.



\textbf{Role:} Applies the state transition function (STF) to batches and generates proofs. \\
\textbf{Language:} Rust \\
\textbf{Key Files:} \texttt{lib/basic\_types/src/}, \texttt{lib/config/src/} \\
\textbf{Inputs:} Sealed batches from the Sequencer. \\
\textbf{Outputs:} State roots, state diffs, and execution traces via gRPC. \\
\textbf{State Maintained:} Local Merkle tree representing account balances. \\
\textbf{Metrics:} Execution time, proof delay. \\
\textbf{Limitations:} Transfer-centric research logic; not a production zkEVM.
