\section{Prover / Mock Prover}
\label{sec:prover}
To allow for scalability experiments without being heavily constrained by the massive hardware requirements of actual cryptographic proof generation, the prototype relies heavily on a mock proving path for analytical benchmarking.

\begin{itemize}
    \item \textbf{Mock Prover Mode:} During benchmark execution, the system uses a parameterized time delay to simulate cryptographic overhead. This allows the study to isolate systems-level bottlenecks (sequencer queue growth, database I/O, network latency) from compute-bound cryptographic constraints.
    \item \textbf{Real Prover Backend:} A basic \texttt{risc0\_prover} path exists in the repository root and is used as the real proof path backend for the executor (\texttt{PROVER\_BACKEND=risc0}). However, it does not implement full parallel PLONK, Groth16, Halo2, Plonky2, or recursive aggregation. Therefore, using the mock prover is the preferred and valid approach for controlled throughput–latency bottleneck isolation.
\end{itemize}
\subsection{Prover Backend Integration and Benchmark-Mode Proof Delay}
The prover path currently supports a \texttt{risc0\_prover} implementation as well as a benchmark-mode mock proof-delay. The benchmark-mode parameterizes the proof generation time to isolate throughput bottlenecks independently of heavy cryptographic computation. Note that the \texttt{risc0\_prover} has a known ELF parse error during guest execution, meaning results relying on this should be treated as benchmark-mode proof-delay unless specifically noted.
